Tutorial_1

### 2024-07-24 Tutorial_1_descriptive_stats/Tutorial_1.Rmd
correct error with resp==0

```{r read-raw-data}
raw <- read_delim(file="Tutorial_1_descriptive_stats/data/DataExp1_6subjects.txt", delim="\t",col_names=T)
head(raw)
tail(raw)
glimpse(raw)
```

@@

```{r wrangle-raw-data}
# remove practice trials
data <- raw %>% filter(practice==0) # 9240 trials: 6 participants x 70 blocks x 22 trials-per-block

# remove unnecessary columns
data <- data %>% select(-c(ss,practice,rd,form,task,primeduration,
                                             blankduration,maskduration,targetduration,
                                             void,target_dir,corresp,resperr))
# remove trials with no response info
sel = which(data$resp==0)
data <- data[-c(sel),] # 9189 rows left

# keep only the no-mask trials
data <- data %>% filter(mask_type == 0) %>%
                 select(-mask_type) # 2737 rows left, and 8 variables

summary(data)
# vp = Versuchsperson or subject
# bl = block number
# tr = trial number within block
# prime_type: no prime (0), consistent prime (1), inconsistent prime (2)
# resp = response left (1) or right (2)
# respac = accuracy
# rt = response time
# TrialNr = trial number within experiment
```

@@

# change relevant variable names (to pid, trial, condition, rt, and acc)
colnames(data_wr) <- c("pid","bl","tr","condition","resp","acc","rt","trial") 
# pid to indicate column with unique person IDs
# trial must be a unique trial number per subject
# condition must be a factor indicating the levels (1,2,...) and labels of the single independent variable 
# rt to indicate column with response times (in ms)
# acc to indicate column with accuracies (1/0)

@@

Load the functions. Make sure you specify the same levels and labels for factor condition in the function plot_eha (line 205) as above (line 83).

@@

```{r create-file-hazard-modeling}
# select the person-trial-bin data set for each subject, unnest them, and select relevant variables.
input_modeling_hazard <- data_final %>% 
                         select(pid, ptb_data) %>%  unnest(ptb_data) %>%
                         select(pid,bl,tr,trial,condition,period,event)
```

>>>>

```{r read-raw-data}
raw <- read_delim(file="Tutorial_1_descriptive_stats/data/DataExp1_6subjects.txt", delim="\t",col_names=T) # 9372 rows
head(raw)
tail(raw)
glimpse(raw)
```

@@

```{r wrangle-raw-data}
# remove practice trials
data <- raw %>% filter(practice==0) # 9240 experimental trials: 6 participants x 70 blocks x 22 trials-per-block

# remove unnecessary columns
data <- data %>% select(-c(ss,practice,rd,form,task,primeduration,
                                             blankduration,maskduration,targetduration,
                                             void,target_dir,corresp,resperr))
# look at trials where resp==0
data %>% filter(resp==0) 
data %>% filter(resp==0) %>% print(n=51)

# remove trials with no response info if rt < 800 (800 was the response deadline in each trial):
# the 46 trials where rt >= 800 and resp==0 are trials in which the subject did not respond; these should not be deleted because they will be treated as right-censored observations in EHA!
# the remaining 5 trials of subject 1 should be removed (for some technical reason the resp (1 or 2) was not recorded; perhaps (s)he pressed both buttons at the same time...)
sel = which(data$resp==0 & data$rt < 800)
data <- data[-c(sel),] # 9235 rows

# keep only the no-mask trials
data <- data %>% filter(mask_type == 0) %>%
                 select(-mask_type) # 2757 rows and 8 variables
summary(data)
# vp = Versuchsperson or subject
# bl = block number
# tr = trial number within block
# prime_type: no prime or blank (0), consistent prime (1), inconsistent prime (2)
# resp = no button (0), button left (1), button right (2) 
# respac = accuracy
# rt = response time
# TrialNr = trial number within experiment
```

@@

# change some variable names to required names (pid, trial, condition, rt, and acc)
colnames(data_wr) <- c("pid","bl","tr","condition","resp","acc","rt","trial") 
# pid to indicate column with unique person IDs
# trial must be a unique trial number per subject
# condition must be a factor indicating the levels (1,2,...) and labels of the single independent variable 
# rt to indicate column with response times (in ms)
# acc to indicate column with accuracies (1/0)

@@

Load the functions. Make sure you specify the same levels and labels for factor condition in the function plot_eha (line 210) as above (line 88).

@@

```{r create-file-hazard-modeling}
# select the person-trial-bin data set for each subject, unnest them, and select relevant variables.
input_modeling_hazard <- data_final %>% 
                         select(pid, ptb_data) %>%  unnest(ptb_data) %>%
                         select(pid,bl,tr,trial,condition,period,event)
summary(input_modeling_hazard)
```
